### 2015-11-20 section/3_redundancy.tex
polish

Note that, \Tool leverages sampling to gain performance with almost \textbf{no}
sacrifice to diagnosis latency or quality, which is
\textbf{different} from traditional sampling techniques
for diagnosing correctness failures \cite{liblit03,liblit05}, where
many more failure runs and hence longer diagnosis latency
are needed to compensate for the performance gain.
The reason is that performance bugs have a unique repetitive nature:
a loop can cause a severe performance problem only when it 
contains many redundant iterations/instances.
Therefore, we can still recognize redundant behavior in just
\textbf{one} failure run, 
as long as the sampling is not insanely sparse
(Section \ref{sec:experiment}). 
%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.

>>>>

Note that, although \Tool uses sampling, its diagnosis is still conducted
in just \textbf{one} run, with almost \textbf{no}
sacrifice to diagnosis latency or quality. This is
\textbf{different} from traditional sampling techniques
for correctness diagnosis \cite{liblit03,liblit05}, where
many more failure runs and hence longer latency
are needed once sampling is enabled.
The reason is that performance bugs have a unique repetitive nature:
a loop can cause a severe performance problem only when it 
contains many redundant iterations/instances.
Therefore, we can still recognize redundant behavior in just
\textbf{one} failure run, 
as long as the sampling is not insanely sparse
(Section \ref{sec:experiment}). 
%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.
